\documentclass[11pt]{article}

% --- arXiv-friendly preamble ---------------------------------------------
% Uses only widely available packages so the source compiles on arXiv's
% TeX Live without modification. Do not introduce custom classes unless
% you also commit them to this directory.
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{microtype}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath,amssymb}
\usepackage{url}
\usepackage{xcolor}
\usepackage[numbers,sort&compress]{natbib}
\usepackage[hidelinks]{hyperref}
\usepackage{cleveref}

% --- Metadata -------------------------------------------------------------
\title{AI-Assisted Hacking: Key to Interoperability or Security Nightmare?}

\author[1]{Florian Krebs%
  \thanks{ORCID: \href{https://orcid.org/0000-0001-6033-801X}{0000-0001-6033-801X}.
  Independent researcher (personal capacity). \textbf{Statement of independence}:
  this is a hobbyist project carried out by the author in a personal capacity.
  It is not part of, endorsed by, funded by, or representative of the views of
  any employer, including the German Aerospace Center (DLR / \textit{Deutsches
  Zentrum f\"ur Luft- und Raumfahrt}). The full statement is in
  \cref{sec:independence}.}}
\affil[1]{Independent researcher (personal capacity)}

\date{\today}

\begin{document}
\maketitle

\begin{abstract}
This paper investigates how modern large language models collapse the traditional
``effort gap'' in reverse engineering. Through two empirical case studies ---
Spider Farmer BLE devices and EcoFlow PowerOcean energy systems --- plus a third
recursive case study of the paper-generation process itself, we show how
AI-assisted analysis turns theoretical protocol knowledge into practical,
replicable local integrations. We then assess whether this collapse is a force
for interoperability and right-to-repair or a systemic security risk, and we
propose a research methodology that treats AI conversation transcripts, vendor
artifacts, and version history as first-class evidence. The dual-use,
\emph{sloppification}, and model-collapse risks of AI-assisted research are
made explicit and mapped to mitigations that the methodology operationalises.
\end{abstract}

% =========================================================================
\section{Introduction and Motivation}
\label{sec:introduction}

\subsection{The effort gap as a security model}
\label{sec:effort-gap}
The dominant security posture for consumer IoT is not cryptographic but
economic: proprietary protocols, obfuscated APKs, and undocumented APIs raise
the activation energy of integration high enough that a casual researcher
gives up. We name this implicit defence the \emph{effort gap} and argue that
it has functioned as the de-facto interoperability barrier of the last decade.

\subsection{Research question}
\label{sec:research-question}
\begin{quote}
Is AI-assisted hacking primarily a means to unlock interoperability, or does
it instead magnify security risk by making obscurity ineffective?
\end{quote}

\subsection{Motivation}
\label{sec:motivation}
\begin{itemize}
  \item \textbf{User sovereignty.} Owners of energy and horticulture hardware
        are increasingly forced into vendor cloud silos for basic local
        control.
  \item \textbf{Right-to-repair and \S{} 69e UrhG / EU 2009/24/EC.} European
        law explicitly permits decompilation for interoperability; AI
        assistance changes the \emph{practical} --- not the \emph{legal} ---
        accessibility of that right. Legal framing to be sourced; see
        \texttt{docs/sources.md} entries S-EF-9, S-EF-10.
  \item \textbf{Dual use.} The same workflow that yields a Home Assistant
        integration yields recovered MQTT credentials and live device write
        paths. The Spider Farmer case study contains a concrete instance of
        recovered live credentials (see \cref{sec:sf-security}).
  \item \textbf{Reproducibility crisis in security research.} Published
        ``hacks'' rarely ship with prompts, transcripts, or commit-pinned
        artifacts. We argue this is now a methodological defect, not a
        stylistic choice.
\end{itemize}

\subsection{Thesis and contributions}
\label{sec:contributions}
We claim that the effort gap has \emph{collapsed asymmetrically}: it has
collapsed faster for interoperability work (where success is verifiable
against a working integration) than for offensive work (which still requires
target selection, persistence, and operational tradecraft). The paper
contributes:
\begin{enumerate}
  \item A definition of the effort gap and an operationalisation as
        measurable KPIs (\texttt{docs/methodology.md} \S 10).
  \item Two empirical case studies with complete artifact provenance
        (\texttt{experiments/spider-farmer/},
        \texttt{experiments/ecoflow-powerocean/}).
  \item An auditable methodology that treats AI conversation transcripts as
        research artifacts, mapped to git history and vendor code
        (\texttt{experiments/*/provenance.md}).
  \item A synthesis of interoperability gains versus dual-use risks, grounded
        in the verified evidence of both cases.
\end{enumerate}

\subsection{Scope and non-goals}
\label{sec:scope}
\begin{itemize}
  \item We do \textbf{not} publish weaponised exploit code; recovered
        credentials are flagged for redaction (\texttt{docs/logbook.md}
        2026-05-01 audit entry).
  \item We do \textbf{not} offer legal advice; AI-generated legal opinions
        in transcripts are flagged as such in \texttt{docs/sources.md} and
        replaced with sourced commentary before any legal claim is made.
  \item We do \textbf{not} evaluate AI models comparatively; the unit of
        analysis is the \emph{workflow}, not the model.
\end{itemize}

% =========================================================================
\section{Methodology}
\label{sec:methodology}

The full operational methodology is maintained in
\texttt{docs/methodology.md}. This section summarises it for the paper and
pins the design decisions that distinguish the work.

\subsection{Unit of analysis: the AI-assisted research workflow}
\label{sec:unit-of-analysis}
A \emph{workflow} is the tuple (vendor artifacts, AI conversation
transcripts, integration code, git history, validation evidence). The case
study, not the device or the model, is the experimental unit.

\subsection{Artifact collection}
\label{sec:artifact-collection}
For each case we vendor:
\begin{itemize}
  \item Vendor binaries and documentation (APKs, PDFs, firmware where
        lawful).
  \item AI conversation transcripts
        (\texttt{raw\_conversations (copy\&paste, web)/}).
  \item Community reference implementations, embedded as plain files for
        direct citation (repo commit \texttt{ffdf60c}).
  \item The integration code under study, embedded under
        \texttt{original/} rather than referenced as a moving submodule.
\end{itemize}

\subsection{Provenance mapping}
\label{sec:provenance-mapping}
Every technical claim is mapped, in a per-case
\texttt{provenance.md}, to (a) the transcript that proposed it, (b) the file
and line numbers in \texttt{original/} that confirm it, and (c) the commit
SHA at which the mapping was verified. Source-register entries carry a
verification status --- \texttt{[repo-vendored]},
\texttt{[repo-referenced]}, \texttt{[unverified-external]},
\texttt{[lit-retrieved]}, \texttt{[lit-read]}, or \texttt{[needs-research]}
--- so the paper can be honest about what has and has not been independently
checked.

\subsection{AI transparency and \emph{lege artis}}
\label{sec:lege-artis}
Following the DFG Guidelines for Safeguarding Good Research
Practice~\citep{dfg2023}, every section discloses where AI assistance was
used and where it was rejected, corrected, or contradicted by the underlying
code. AI-generated legal analysis is never used as legal advice. The
repository's AI policy is canonicalised in
\texttt{CLAUDE\_CODE\_INSTRUCTIONS.md} and aliased in
\texttt{.instructions.md} and \texttt{copilot-instructions.md}.

\subsection{KPIs (effort-gap operationalisation)}
\label{sec:kpis}
Drawn from \texttt{docs/methodology.md} \S 10 and applied per case study:
\begin{itemize}
  \item \textbf{Process:} artifact-acquisition completeness, prompt-iteration
        count, automation ratio.
  \item \textbf{Experimental success:} probe success rate, functional
        coverage, reproducibility score.
  \item \textbf{Time and effort:} time-to-first-working-integration,
        effort-gap metric (estimated manual hours vs.\ AI-assisted hours).
  \item \textbf{Problem characterisation:} discovery density, candidate-space
        size, obscurity depth.
\end{itemize}

\subsection{Validation and reproducibility}
\label{sec:validation}
Each finding is reproduced against the embedded \texttt{original/} code at a
pinned commit. Failed attempts are recorded in the logbook and (where
applicable) in the per-case \texttt{provenance.md}. The KPI table at the end
of each case study reports verified, not aspirational, numbers.

\subsection{Ethics}
\label{sec:ethics}
The dual-use evaluation is part of the methodology, not a postscript. For
each case we explicitly enumerate (a) what becomes easier for an integrator
and (b) what becomes easier for an attacker. Live credentials, device
serials, and broker IPs are flagged for redaction before any public release
(\texttt{docs/logbook.md} 2026-05-01 audit).

% =========================================================================
\section{Experiment \& Analysis 1 --- Spider Farmer}
\label{sec:case-spider-farmer}

\subsection{System and threat model}
\label{sec:sf-threat-model}
Spider Farmer GGS controllers, power strips, lamps, and grow tents
communicate locally over BLE and remotely via an MQTT cloud broker. The
vendor's defence is an AES-128-CBC scheme with hardcoded keys and IVs
embedded in the Android APK, plus a self-signed-cert MQTT broker.

\subsection{Artifact inventory}
\label{sec:sf-artifacts}
Source register entries S-SF-1 through S-SF-8. Primary artifacts:
\begin{itemize}
  \item \texttt{original/doc/Spider Farmer\_2.3.0\_APKPure.zip},
        \texttt{Spider Farmer\_2.4.0\_APKPure.zip}.
  \item Three independent reference implementations (ESPHome,
        ESP32\,$\to$\,MQTT bridge, Python\,+\,MQTT).
  \item \texttt{raw\_conversations (copy\&paste, web)/} (7 transcripts).
  \item The integration itself, embedded at \texttt{original/}
        (manifest version \texttt{3.0.0},
        \texttt{config\_flow.py} \texttt{VERSION = 3}).
\end{itemize}

\subsection{AI-assisted analysis workflow}
\label{sec:sf-workflow}
\begin{enumerate}
  \item \textbf{APK static extraction} of strings, action fields, and
        constants.
  \item \textbf{Cross-implementation comparison} across four independent
        reverse-engineering attempts, captured in
        \texttt{original/doc/apk\_analysis/implementations.md}.
  \item \textbf{AI-mediated reconciliation} of conflicting key/IV
        candidates (transcripts T1--T6).
  \item \textbf{Code-level confirmation} against the integration's
        \texttt{const.py}, \texttt{ble\_protocol.py},
        \texttt{ble\_coordinator.py}, and \texttt{\_\_init\_\_.py}.
\end{enumerate}

\subsection{Findings --- interoperability}
\label{sec:sf-interop}
\begin{itemize}
  \item BLE service \texttt{000000ff-0000-1000-8000-00805f9b34fb};
        characteristics \texttt{0000ff01} (notify) and \texttt{0000ff02}
        (write-with-response).
  \item AES-128-CBC with zero padding; two-stage header with CRC16-Modbus.
  \item Static outgoing IVs per device type, dynamic incoming IVs derived
        from the packet header --- confirmed in
        \texttt{ble\_protocol.py} lines 195--204.
  \item Corrected key/IV pairs for the CB controller and friends, pinned in
        \texttt{const.py} lines 45--47.
  \item Concurrent-write safety via \texttt{asyncio.Lock} in
        \texttt{ble\_coordinator.py} line 79.
  \item Migration framework \texttt{async\_migrate\_entry} in
        \texttt{\_\_init\_\_.py} line 95; the integration is now at
        \texttt{VERSION = 3} past the T4-era \texttt{1\,$\to$\,2}
        migration (the \texttt{2\,$\to$\,3} step is presently undocumented
        by any preserved transcript --- recorded as an open issue).
\end{itemize}

\subsection{Validation}
\label{sec:sf-validation}
Each constant and code path above was re-checked against
\texttt{original/} at commit \texttt{ffdf60c} (logbook entry ``audit against
embedded vendor code''). The four independent implementations agree on the
BLE protocol shape; minor disagreements on key tables were resolved in
favour of the in-tree \texttt{const.py}.

\subsection{Findings --- security implications}
\label{sec:sf-security}
The \texttt{original/doc/log.md} community thread documents a
self-signed-certificate MITM against the vendor MQTT broker
\texttt{sf.mqtt.spider-farmer.com:8333}, recovering live credentials
(username \texttt{sf\_ggs\_cb}; password redacted in the published paper,
present in S-SF-5). This is independent corroboration of the claim that the
effort gap has collapsed for \emph{both} defenders and attackers.

\subsection{KPI summary (Spider Farmer)}
\label{sec:sf-kpis}
\emph{To be populated from logbook and provenance evidence}:
artifact-acquisition completeness, transcript count (7),
independent-implementation count (3 + integration),
time-to-first-working-integration, residual obscurity depth.

% =========================================================================
\section{Experiment \& Analysis 2 --- EcoFlow PowerOcean}
\label{sec:case-ecoflow}

\subsection{System and threat model}
\label{sec:ef-threat-model}
The EcoFlow PowerOcean is a residential energy system --- 12\,kW inverter,
two 5\,kWh batteries, 11\,kW PowerPulse charger (per
\texttt{original/doc/equipment.md} and \texttt{REPORT.md} \S 9). It exposes
three API surfaces: a legacy \texttt{setDeviceProperty} REST endpoint, the
published Open API (\texttt{PUT /iot-open/sign/device/quota} with
HMAC-SHA256), and an MQTT surface. The vendor publishes documentation for
the Open API but the consumer app uses the legacy endpoint.

\subsection{Artifact inventory}
\label{sec:ef-artifacts}
Source register entries S-EF-1 through S-EF-6. Primary artifacts:
\begin{itemize}
  \item \texttt{original/doc/EcoFlow\_6.13.8.2\_APKPure/} --- four APK split
        files plus manifest.
  \item \texttt{original/doc/ecoflow-open-demo.zip} --- vendor reference
        Java implementation.
  \item \texttt{original/doc/powerocean.pdf}, \texttt{geninfo.pdf} ---
        vendor documentation.
  \item \texttt{original/doc/apk.md} (327 lines), \texttt{apk-logs.md}
        (546 lines), \texttt{implementation.md} (434 lines), six raw
        extraction logs.
  \item The integration \texttt{powerocean\_dev} at \texttt{manifest.json}
        version \texttt{2026.05.01}, embedded at \texttt{original/}.
        Upstream parent \url{https://github.com/niltrip/powerocean} per
        \texttt{const.py} line 13.
  \item \texttt{raw\_conversations (copy\&paste, web)/} (3 transcripts).
\end{itemize}

\subsection{AI-assisted analysis workflow}
\label{sec:ef-workflow}
\begin{enumerate}
  \item \textbf{APK string and action-field extraction} to enumerate
        writeable parameters.
  \item \textbf{Three-surface reconciliation} --- \texttt{apk.md} line 52
        documents the choice to use the legacy endpoint over the Open API,
        resolving the prior open question.
  \item \textbf{Type-system bug discovery} --- the regex
        \texttt{(?<!st)(amp|current)\$} (\texttt{types.py} line 90) corrects
        a misclassification that conflated current readings with the literal
        ``st'' suffix.
  \item \textbf{Config-flow refactor} --- three-step config flow
        (\texttt{config\_flow.py}, 510 lines) with cross-domain
        \texttt{async\_step\_import} migration.
\end{enumerate}

\subsection{Findings --- interoperability}
\label{sec:ef-interop}
\begin{itemize}
  \item Write surface: \texttt{POST /iot-devices/device/setDeviceProperty}
        with payload
        \texttt{\{"sn": "<device\_sn>", "params": \{"<camelCase\_field>":
        <value>\}\}} --- confirmed at \texttt{api.py} line 306.
  \item Field-name convention: predictable camelCase from APK constants
        (e.g.\ \texttt{ACTION\_W\_CFG\_BACKUP\_REVERSE\_SOC}\,$\to$\,
        \texttt{cfgBackupReverseSoc}).
  \item New writeable HA entities: \texttt{button.system\_reboot},
        \texttt{button.system\_selfcheck},
        \texttt{number.backup\_reserve\_soc},
        \texttt{number.fast\_chg\_max\_soc},
        \texttt{number.charger\_power\_limit},
        \texttt{number.grid\_in\_pwr\_limit}.
  \item Domain \texttt{powerocean\_dev} (\texttt{const.py} line 10),
        HACS/hassfest conformance per \texttt{REPORT.md} \S 5.3.
\end{itemize}

\subsection{Validation}
\label{sec:ef-validation}
Every constant and endpoint above was re-checked against
\texttt{original/} at commit \texttt{ffdf60c}. The three-surface model is
documented in-tree, not inferred.

\subsection{Findings --- security implications}
\label{sec:ef-security}
\begin{itemize}
  \item The legacy endpoint accepts authenticated writes without the
        HMAC-SHA256 ceremony of the Open API. Any leaked session token
        grants the same write surface used by the consumer app.
  \item Writeable parameters include grid-in power limit, battery reserve
        SOC, and EV charger power. The dual-use surface is non-trivial: the
        same controls that enable local automation enable remote
        denial-of-availability against a residential energy system.
  \item Vendor APK and PDF redistribution status is flagged in
        \texttt{docs/sources.md} (S-EF-2, S-EF-3, S-EF-4) and must be
        resolved before public release.
\end{itemize}

\subsection{KPI summary (EcoFlow PowerOcean)}
\label{sec:ef-kpis}
\emph{To be populated}: number of writeable parameters discovered,
transcript count (3), API-surface count (3), residual obscurity depth,
time-to-first-working-write.

% =========================================================================
\section{Experiment \& Analysis 3 --- The paper as an AI-assisted artifact}
\label{sec:case-meta}

\subsection{System and threat model}
\label{sec:meta-threat-model}
The unit of analysis here is recursive: the paper that documents AI-assisted
reverse engineering is itself an AI-assisted artifact. The ``system'' is the
paper-generation pipeline: prompts, AI conversation transcripts, repository
state, and the human researcher in the loop. Specific risks to evaluate are:
\begin{itemize}
  \item \textbf{Fabricated citations.} LLMs are known to hallucinate
        references; an entry surfaced from a database is not the same as a
        paper that has been read.
  \item \textbf{Silent memorisation / plagiarism.} AI-drafted prose may
        reproduce training-data text without attribution.
  \item \textbf{Prompt injection.} Vendor APK strings, community-thread
        excerpts, and PDF contents embedded under
        \texttt{experiments/*/original/} are read by the agent and could in
        principle inject instructions.
  \item \textbf{Misrepresentation of source claims.} A Consensus-surfaced
        abstract is not a peer-reviewed claim until the full text has been
        read.
  \item \textbf{Tooling drift.} Identical prompts in later sessions produce
        non-identical outputs.
  \item \textbf{AI-generated legal opinion mistaken for sourced legal
        commentary.} A specific instance from the EcoFlow transcripts has
        already been flagged; the failure mode is generalisable.
\end{itemize}

\subsection{Artifact inventory}
\label{sec:meta-artifacts}
The case-study artifacts are vendored under
\texttt{experiments/paper-meta-process/} with the same shape as the other
two case studies (\texttt{README.md}, \texttt{REPORT.md},
\texttt{provenance.md}, \texttt{raw\_conversations (copy\&paste, web)/}):
\begin{itemize}
  \item The git history of this repository on \texttt{main} and on the
        development branch \texttt{claude/develop-paper-structure-7lG2s}.
  \item Conversation transcripts of paper-development sessions, preserved
        in \texttt{experiments/paper-meta-process/raw\_conversations
        (copy\&paste, web)/}. Each transcript declares a verification
        status (\texttt{[verbatim-export]} /
        \texttt{[curated-reconstruction]} / \texttt{[redacted]}) in its
        YAML header. The first preserved transcript
        (\texttt{T1-paper-structure-and-literature.md}) is a
        \texttt{[curated-reconstruction]} of the 2026-05-01 session that
        produced the paper structure, the literature pass, the FAIR
        metadata, and this case study.
  \item The case-study report
        \texttt{experiments/paper-meta-process/REPORT.md} and the
        per-transcript provenance map
        \texttt{experiments/paper-meta-process/provenance.md} (parallel
        to the Spider Farmer and EcoFlow \texttt{provenance.md} files).
  \item The repository AI policy: \texttt{CLAUDE\_CODE\_INSTRUCTIONS.md},
        \texttt{.instructions.md}, \texttt{copilot-instructions.md},
        \texttt{CLAUDE.md}.
  \item The executable research-protocol agent prompt
        (\texttt{docs/research-protocol-prompt.md}).
  \item The methodology document (\texttt{docs/methodology.md}) and its KPI
        framework (\S 10).
  \item The literature register in \texttt{docs/sources.md} with the
        verification-status legend (\texttt{[repo-vendored]},
        \texttt{[repo-referenced]}, \texttt{[unverified-external]},
        \texttt{[lit-retrieved]}, \texttt{[lit-read]},
        \texttt{[needs-research]}).
  \item The logbook (\texttt{docs/logbook.md}), updated per commit per the
        rule established on 2026-05-01.
  \item The arXiv-ready LaTeX build pipeline (\texttt{paper/main.tex},
        \texttt{paper/Makefile},
        \texttt{.github/workflows/build-paper.yml}).
  \item The mirroring rule between \texttt{paper/main.md} and
        \texttt{paper/main.tex} (rule 11 in
        \texttt{CLAUDE\_CODE\_INSTRUCTIONS.md}).
  \item FAIR / citation metadata at the repository root:
        \texttt{CITATION.cff}, \texttt{.zenodo.json},
        \texttt{codemeta.json}, plus the FAIR-mapping document
        \texttt{docs/fair.md}.
\end{itemize}

\subsection{AI-assisted analysis workflow}
\label{sec:meta-workflow}
\begin{enumerate}
  \item \textbf{Repo-context loading.} The agent reads
        \texttt{CLAUDE\_CODE\_INSTRUCTIONS.md},
        \texttt{docs/methodology.md},
        \texttt{docs/logbook.md}, and the per-case
        \texttt{provenance.md} files at session start.
  \item \textbf{Skeleton generation.} Section structure proposed by the AI
        from the verified case-study evidence (commit \texttt{ffdf60c}) and
        reviewed by the researcher.
  \item \textbf{Iterative prompting.} Each user turn maps to one or more
        commit-grouped edits. The conversation transcript is the
        source-of-truth log.
  \item \textbf{Structured literature search.} External academic-database
        queries (Consensus / Semantic Scholar / arXiv) batched per the
        tool's rate-limit guidance; results recorded with
        \texttt{[lit-retrieved]} status.
  \item \textbf{Mirror enforcement.} Any change to \texttt{paper/main.md}
        must be reflected in \texttt{paper/main.tex} before commit (rule
        11).
  \item \textbf{Git-paired logbook entries.} Each meaningful commit has a
        paired logbook entry naming the action, files touched, decisions,
        open issues, and next steps.
\end{enumerate}

\subsection{Findings --- interoperability and reproducibility}
\label{sec:meta-interop}
\begin{itemize}
  \item The paper, including every claim in \cref{sec:case-spider-farmer}
        and \cref{sec:case-ecoflow}, is regenerable from the repository
        state at the pinned commit \texttt{ffdf60c} for the vendor evidence
        and at the head of the development branch for the prose.
  \item The verification-status legend makes the read-state of every cited
        source explicit and prevents \texttt{[lit-retrieved]} entries from
        drifting into the paper as if they had been read.
  \item The arXiv build pipeline reproduces the PDF and submission tarball
        deterministically from \texttt{paper/main.tex} plus
        \texttt{paper/references.bib}.
  \item The methodology (\cref{sec:methodology}) and KPI framework
        (\texttt{docs/methodology.md} \S 10) are themselves operationalised
        as the executable agent prompt
        (\texttt{docs/research-protocol-prompt.md}), making the research
        protocol a runnable artifact rather than only a description.
\end{itemize}

\subsection{Validation}
\label{sec:meta-validation}
\begin{itemize}
  \item All \cref{sec:case-spider-farmer} and
        \cref{sec:case-ecoflow} claims were re-checked against the embedded
        vendor code at commit \texttt{ffdf60c} (logbook entry ``audit
        against embedded vendor code'').
  \item All literature entries from the 2026-05-01 search session are
        marked \texttt{[lit-retrieved]}, not \texttt{[lit-read]} ---
        explicitly capturing the gap between database-surfaced and
        read-in-full.
  \item The mirroring rule between \texttt{paper/main.md} and
        \texttt{paper/main.tex} is enforced by reviewer attention at
        commit time and by CI
        (\texttt{.github/workflows/build-paper.yml}), which rebuilds the
        PDF on every paper-touching commit and surfaces LaTeX-syntactic
        regressions.
  \item AI-generated legal opinions in transcripts are explicitly flagged
        (\texttt{docs/sources.md} S-EF-9) and held out of the paper until
        replaced with sourced legal commentary.
\end{itemize}

\subsection{Findings --- security and dual-use implications}
\label{sec:meta-security}
\begin{itemize}
  \item \textbf{Fabricated citations.} All $\sim$50 entries in the
        literature register are \texttt{[lit-retrieved]} only. Any upgrade
        to \texttt{[lit-read]} without the researcher actually reading the
        paper would be a fabrication. The empirical base rates make this
        concrete: Walters \& Wilder (2023) found \textbf{55\% of
        ChatGPT-3.5 and 18\% of GPT-4 generated citations were fabricated}
        in literature reviews, with a further 24--43\% of the \emph{real}
        citations carrying substantive errors (\texttt{docs/sources.md}
        L-SLOP-1). McGowan et al.\ (2023) found only \textbf{2 of 35}
        ChatGPT-generated psychiatry citations were real (L-SLOP-4).
        Chelli et al.\ (2024) measured hallucination rates of
        28.6\%--91.4\% across LLMs in systematic-review reference
        generation (L-SLOP-2). These are not edge cases.
  \item \textbf{AI-generated legal analysis.} A specific opinion in
        transcript T3 line 147 (EcoFlow) is flagged in
        \texttt{docs/sources.md} and \cref{sec:disc-r2r} --- without that
        flag, it would have entered the paper as if sourced.
  \item \textbf{Live-credential leakage.} \texttt{docs/sources.md} S-SF-5
        carries the recovered MQTT credentials for the Spider Farmer
        broker. These must be redacted before public release of the paper.
        This redaction is the single most important pre-publication action
        and is recorded as an open issue in the logbook.
  \item \textbf{Prompt injection from imported artifacts.} Vendor APK
        strings, PDF contents, and community-thread excerpts under
        \texttt{experiments/*/original/} are read by the AI agent. The
        mitigation is the AI policy's labelling requirement plus
        researcher verification of every AI-attributed claim.
  \item \textbf{Tooling drift.} The workflow and committed artifacts are
        the reproducible unit; the AI's exact tokens are not.
\end{itemize}

\subsection{KPI summary (Meta-process)}
\label{sec:meta-kpis}
\emph{To be populated}: number of commits on the paper-development branch,
number of AI sessions logged in \texttt{docs/logbook.md}, ratio of
AI-generated to researcher-authored prose, count of AI-generated claims
subsequently flagged or removed, count of \texttt{[lit-retrieved]} entries
upgraded to \texttt{[lit-read]}, time-to-first-publishable-draft.

% =========================================================================
\section{Synthesis}
\label{sec:synthesis}

\subsection{Cross-case comparison}
\label{sec:synthesis-table}

\begin{table}[h]
\centering
\footnotesize
\begin{tabular}{p{2.6cm} p{3.6cm} p{3.6cm} p{3.6cm}}
\toprule
\textbf{Dimension} & \textbf{Spider Farmer} & \textbf{EcoFlow PowerOcean} & \textbf{Meta-process (this paper)} \\
\midrule
Defence model
  & Hardcoded AES keys/IVs in APK + self-signed MQTT cert
  & Three undocumented API surfaces; vendor publishes only one
  & None --- the artifact is open by construction \\
Primary AI lift
  & Reconciling four independent implementations
  & Discovering and choosing among API surfaces; type-system bug fix
  & Skeleton generation, structured literature retrieval, mirror discipline \\
Independent corroboration
  & 3 community implementations + community MITM thread
  & 1 vendor reference implementation + 1 upstream community fork
  & Git history; researcher review at commit time; CI build \\
Live credential recovery
  & Yes (MQTT broker creds)
  & No (token-bearer model)
  & N/A --- the paper is the artifact \\
Dual-use blast radius
  & Per-device control over horticulture hardware
  & Grid-in / battery-reserve / EV-charger control
  & Fabricated citations; unsourced legal opinions; redaction failures \\
Status of vendor public docs
  & None
  & Open API documented; consumer app uses different surface
  & All policy and provenance documented in repo \\
\bottomrule
\end{tabular}
\caption{Cross-case comparison of the three AI-assisted case studies in
this paper. The third column is the recursive meta-process case study
introduced in \cref{sec:case-meta}.}
\label{tab:cross-case}
\end{table}

\subsection{What the AI workflow added}
\label{sec:synthesis-ai-lift}
\begin{itemize}
  \item \textbf{Spider Farmer.} Not protocol \emph{discovery} --- the four
        community implementations had already done that --- but
        \emph{reconciliation} across conflicting key tables and verification
        of the dynamic-IV slice formula.
  \item \textbf{EcoFlow PowerOcean.} Surface enumeration and field-name
        convention recovery: a manual reverse-engineer would have eventually
        found the legacy endpoint, but the AI-assisted workflow recovered
        the full writeable-parameter catalogue from APK constants in a
        single pass.
  \item \textbf{Meta-process.} Skeleton generation from sparse evidence,
        structured literature retrieval at scale, and the disciplined
        application of verification-status labels to keep the paper honest
        about what it has and has not read.
\end{itemize}

\subsection{Common patterns}
\label{sec:synthesis-patterns}
\begin{itemize}
  \item All three defences/processes relied on the \emph{combination} of
        obscurity and effort, not on either alone --- and in the
        meta-process, on the \emph{combination} of access control and
        labour, where the labour is the researcher reading and verifying.
  \item All three yielded clean outputs once a single organising piece of
        evidence (key table; API surface; verification-status legend) was
        identified.
  \item In all three cases, AI assistance compressed the \emph{organisation
        and reconciliation} phase far more than the \emph{discovery}
        phase. The effort-gap collapse is unevenly distributed across
        workflow stages.
\end{itemize}

\subsection{Limits of the comparison}
\label{sec:synthesis-limits}
Three cases is still small. The meta-process case is also recursive ---
the paper documenting AI-assisted reverse engineering is itself an
AI-assisted artifact, which means selection bias and tooling drift apply
to its analysis the same way they apply to the integration cases. We
treat the meta-process case as evidence for the methodology, not as
independent confirmation of the central thesis.

% =========================================================================
\section{Discussion}
\label{sec:discussion}

\subsection{Interoperability: the automated right to repair}
\label{sec:disc-r2r}
European decompilation-for-interoperability provisions
(\S{} 69e UrhG, EU 2009/24/EC) presuppose that decompilation is
\emph{legally} possible for an end user. AI assistance makes it
\emph{practically} possible. The case studies are existence proofs that the
legal carve-out can now be exercised at hobbyist scale, not just by
specialised firms. Whether legislatures intended this is an empirical
question for legal scholarship, not for this paper. (Sourcing:
\texttt{docs/sources.md} S-EF-9, S-EF-10, both
\texttt{[unverified-external]} until cross-checked.)

\subsection{The collapse of the boredom barrier}
\label{sec:disc-boredom}
Security through obscurity rested on a labour-market assumption: that a
determined hobbyist would not invest a fortnight to integrate a grow-tent
controller. That assumption is dead. The Spider Farmer case shows three
independent community implementations of the same protocol and an
independently recovered set of MQTT credentials --- converging evidence that
the obscurity barrier has perforated.

\subsection{Asymmetry of collapse}
\label{sec:disc-asymmetry}
The effort gap has \emph{not} collapsed uniformly. AI assistance compresses
the \emph{known-good-protocol} path far more than the
\emph{novel-vulnerability} path; verifying an integration against a live
device is cheap, and verifying an exploit against a live target is not. We
argue this asymmetry is the most under-discussed feature of the post-LLM
threat model.

\subsection{Dual-use accountability}
\label{sec:disc-dual-use}
Both case studies expose live attack surfaces. In Spider Farmer the surface
is already public --- recovered in a community thread --- and the case is a
\emph{post-hoc} documentation of a collapse that has already happened. In
EcoFlow the surface is documented for the first time here, and we
accordingly enumerate the redactions that must be applied before public
release (logbook 2026-05-01 audit;
\texttt{docs/sources.md} S-SF-5, S-EF-2..4).

\subsection{The paper as evidence for its own thesis}
\label{sec:disc-recursion}
The meta-process case (\cref{sec:case-meta}) is recursive evidence for
our central claim. The same pipeline that compresses the Spider Farmer
and EcoFlow integrations compresses paper-writing --- and exposes the
same dual-use surface. Just as recovered MQTT credentials are a
side-effect of integration work, fabricated citations and unsourced
legal opinions are side-effects of paper work. The discipline that
resolves both is the same: pin artifacts, label provenance, treat AI
output as evidence to be verified rather than as authority.

\subsection{Sloppification: the AI methodological discount}
\label{sec:disc-sloppification}
The most concrete and under-managed risk of AI-assisted research is what
we call the \emph{methodological discount} --- the unspoken trade-off in
which a researcher accepts a degraded standard of evidence in exchange
for AI-assisted speed. Empirical work on LLMs in scientific writing now
documents this risk concretely:
\begin{itemize}
  \item Walters \& Wilder (2023), \emph{Scientific Reports}, found that
        \textbf{55\% of GPT-3.5 and 18\% of GPT-4 generated citations
        were fabricated} in literature reviews, with a further substantial
        fraction of \emph{real} citations carrying substantive errors
        (\texttt{docs/sources.md} L-SLOP-1).
  \item McGowan et al.\ (2023), \emph{Psychiatry Research}, found only
        \textbf{2 of 35} ChatGPT-generated psychiatry citations were
        real; the remaining 33 were either subtly wrong or pastiches of
        existing manuscripts (L-SLOP-4).
  \item Chelli et al.\ (2024), \emph{JMIR}, measured hallucination rates
        of 28.6\%--91.4\% and recall rates as low as 11.9\% across LLMs
        in systematic-review reference generation (L-SLOP-2).
  \item Buchanan \& Hill (2023) document $>$30\% non-existent citations
        in ChatGPT outputs across the \emph{Journal of Economic
        Literature} topic taxonomy (L-SLOP-3).
  \item Suchak et al.\ (2025), \emph{PLOS Biology}, document a real-world
        consequence: NHANES-based formulaic single-factor papers grew
        from 4 per year (2014--2021) to \textbf{190 in the first ten
        months of 2024} --- direct evidence of paper-mill / AI-assisted
        output flooding the literature (L-SLOP-8).
  \item Kendall \& Teixeira da Silva (2023), \emph{Learned Publishing},
        and Sabel et al.\ (2025, \emph{Royal Society Open Science}, the
        Stockholm Declaration) frame this at the system level: paper
        mills are now AI-assisted at industrial scale, and the
        publishing model needs structural reform (L-SLOP-5, L-SLOP-7).
\end{itemize}
The mitigation we operationalise is mundane: a verification-status
legend (\texttt{[lit-retrieved]} / \texttt{[lit-read]}) that makes the
read-state of every cited source explicit, plus a refusal to upgrade an
entry without the researcher actually reading the paper.
Sloppification is not solved by a better model; it is solved by labour
discipline that the model cannot perform.

\subsection{Model collapse and the dilution of the scientific commons}
\label{sec:disc-model-collapse}
A second, longer-horizon argument cuts in the opposite direction.
Shumailov et al.\ (2024, \emph{Nature}) showed that \textbf{AI models
trained recursively on AI-generated content collapse} --- the tails of
the original distribution disappear and successive generations of models
forget the genuine human-data signal (L-MC-1, L-MC-7). Seddik et al.\
(2024) prove this is unavoidable when training is purely synthetic but
bounded when synthetic and real data are mixed below a threshold
(L-MC-3). Gerstgrasser et al.\ (2024) extend this further:
\emph{accumulating} real and synthetic data over time (rather than
replacing real with synthetic) can avoid collapse entirely, with a
finite test-error upper bound independent of iteration count (L-MC-4).
Suresh et al.\ (2024) characterise the \emph{rate} of collapse for
fundamental distributions (L-MC-5); ForTIFAI / Shabgahi et al.\ (2025)
propose confidence-aware training objectives that delay collapse onset
by $>$2.3$\times$ (L-MC-2).

The connection to our work is direct. Each AI-assisted paper that ships
\emph{un-verified} AI output into the corpus dilutes the ground-truth
signal that future models will be trained on. The two failure modes
--- sloppification at the paper level and model collapse at the corpus
level --- are the same problem at different timescales. They share a
single mitigation: \textbf{preserve the provenance of human-verified,
ground-truth content and keep it cleanly distinguishable from
AI-generated content}. The literature points to a small set of
practices that work against the dilution:
\begin{itemize}
  \item \textbf{Provenance and read-state labelling at the artifact
        level} --- what \texttt{docs/sources.md} does for citations.
  \item \textbf{Conversation-transcript preservation} --- what
        \texttt{experiments/*/raw\_conversations (copy\&paste, web)/}
        does for AI contributions.
  \item \textbf{Pinning external evidence by commit SHA} --- what the
        \texttt{ffdf60c} audit does for vendor code.
  \item \textbf{Mixing rather than replacing}: keep human-authored data
        alongside AI-assisted output rather than letting the AI output
        substitute for it (L-MC-3, L-MC-4).
  \item \textbf{Disclosure and detection at the publication level} ---
        guidelines from Cheng et al.\ (2025) and Pellegrina et al.\
        (2025); Stockholm Declaration governance proposals from Sabel
        et al.\ (2025) (L-SLOP-7, L-SLOP-10, L-SLOP-12).
  \item \textbf{Filtering high-confidence-token artifacts} during model
        training --- ForTIFAI (L-MC-2); not actionable for paper
        authors but actionable for foundation-model trainers.
\end{itemize}
We do not claim to solve model collapse. We claim that the methodology
in \cref{sec:methodology} is consistent with what the literature
suggests works against it, and that publishing AI-assisted research
without provenance and disclosure is, at the corpus level, an
externality on every future model.

\subsection{Methodological implications for security research}
\label{sec:disc-methodology}
\begin{itemize}
  \item Treat AI conversation transcripts as research artifacts. They are
        the equivalent of a lab notebook for the LLM era.
  \item Pin all external code by commit SHA, not by branch name. Branches
        move; SHAs do not.
  \item Embed vendor artifacts under explicit redistribution caveats rather
        than referencing moving URLs.
  \item Mark every literature claim with a verification status. The
        discipline is cheap; the alternative is the current state of
        practice (\cref{sec:disc-sloppification}).
  \item Disclose AI usage explicitly. The disclosure is not an apology
        --- it is the unit of accountability that lets the work be
        audited rather than guessed at.
\end{itemize}

\subsection{Threats to validity}
\label{sec:disc-threats}
\begin{itemize}
  \item \textbf{Selection bias.} Cases were chosen because the researcher
        already wanted local control; failed attempts at harder targets are
        under-reported.
  \item \textbf{Tooling drift.} AI model behaviour changes between
        sessions. The workflow is reproducible against artifacts; identical
        AI outputs are not.
  \item \textbf{Legal framing.} AI-generated legal analysis in transcripts
        is not legal advice and is flagged as such in the source register.
  \item \textbf{Redistribution.} Vendor APKs and PDFs are vendored for
        cite-ability but their redistribution status is not yet resolved.
  \item \textbf{Sloppification risk in this paper.} The literature
        register (\cref{sec:meta-security},
        \cref{sec:disc-sloppification}) is currently
        \texttt{[lit-retrieved]} only. No claim in this paper depends
        on a literature citation that has not been read in full by the
        researcher; we have explicitly preferred to leave a claim
        unsupported rather than cite a paper we have not read.
\end{itemize}

% =========================================================================
\section{Conclusion}
\label{sec:conclusion}

AI-assisted reverse engineering does not invent new capabilities; it lowers
the activation energy of capabilities that already existed. The Spider
Farmer and EcoFlow PowerOcean cases show that this lowering is enough to
collapse the effort gap that previously sustained ``security through
obscurity'' as a viable consumer-IoT defence. The collapse is genuinely
double-edged --- it materially advances right-to-repair while exposing live
attack surfaces --- but it is also \emph{asymmetric}, compressing the
integration path more aggressively than the offensive path.

The path forward is not to discourage AI-assisted research but to make it
\emph{auditable}: vendor artifacts pinned, transcripts treated as evidence,
dual-use evaluation built into the methodology rather than appended to it,
and legal framing always sourced. Obscurity is dead. What replaces it has
to be designed, not assumed.

\subsection{Future work}
\label{sec:future-work}
\begin{itemize}
  \item Extend to a fourth case study in a domain with no prior
        community integration (open question: does the asymmetry
        hypothesis hold there?).
  \item Operationalise the effort-gap KPIs against historical
        reverse-engineering case studies for a longitudinal comparison.
  \item Develop a responsible-disclosure framework specific to AI-assisted
        reverse engineering.
  \item Replace \texttt{[unverified-external]} legal sources with sourced
        commentary; address \texttt{[needs-research]} items in
        \texttt{docs/sources.md}.
  \item Reconstruct the Spider Farmer
        \texttt{VERSION 2\,$\to$\,3} migration step that no preserved
        transcript currently documents.
  \item Read in full the \texttt{[lit-retrieved]} literature in
        \texttt{docs/sources.md} clusters A--J and upgrade entries to
        \texttt{[lit-read]} before any of them is cited as authority
        rather than as a database pointer.
\end{itemize}

% =========================================================================
\section{AI usage disclosure and disclaimer}
\label{sec:ai-disclosure}

\subsection{Models and tooling}
\label{sec:ai-disclosure-models}
This paper was developed with Claude (Opus 4.7 model family) by
Anthropic, running in the Claude Code CLI~\citep{anthropic2026claude}.
Specific session details, model versions, and conversation transcripts
are committed under \texttt{experiments/*/raw\_conversations
(copy\&paste, web)/} (notably
\texttt{experiments/paper-meta-process/raw\_conversations (copy\&paste,
web)/T1-paper-structure-and-literature.md}) and referenced in
\texttt{docs/logbook.md}. Structured literature retrieval was performed
via the Consensus academic-database front end (Semantic Scholar /
PubMed / Scopus / arXiv); the queries used and the candidate citations
they returned are recorded in \texttt{docs/sources.md} clusters A--J.

\subsection{Division of labour}
\label{sec:ai-disclosure-division}
\begin{itemize}
  \item \textbf{Researcher (human).} Research question, case selection,
        ethical and redaction decisions, validation against vendor code
        at commit \texttt{ffdf60c}, and final acceptance of every
        paragraph.
  \item \textbf{AI assistant (Claude).} Skeleton drafting, structured
        literature retrieval, cross-case comparison, prose tightening,
        LaTeX rendering, and methodology operationalisation as the
        executable agent prompt
        (\texttt{docs/research-protocol-prompt.md}).
  \item \textbf{Hybrid.} Provenance maps
        (\texttt{experiments/*/provenance.md}), source register
        (\texttt{docs/sources.md}), logbook entries, and KPI scaffolding
        --- AI drafted, researcher verified or flagged.
\end{itemize}

\subsection{What is and is not sourced}
\label{sec:ai-disclosure-sourcing}
\begin{itemize}
  \item All technical claims in \cref{sec:case-spider-farmer} and
        \cref{sec:case-ecoflow} are sourced to vendor code at commit
        \texttt{ffdf60c} and to specific transcript line numbers;
        verifiable by re-running the audit described in
        \texttt{docs/logbook.md} (entry ``audit against embedded vendor
        code'').
  \item All literature in \texttt{docs/sources.md} clusters A--J
        (covering LLM-assisted RE, vulnerability/exploit generation,
        hardcoded secrets, BLE/IoT obscurity, right-to-repair,
        local-first smart home, DMCA \S 1201(f), counter-positions,
        sloppification of science, and model collapse) is currently
        \texttt{[lit-retrieved]} --- the entries were surfaced from a
        structured database query but the full texts have not been read
        by the researcher. \textbf{No claim in this paper depends on a
        literature citation that has not been read in full.} Where the
        literature is invoked, it is invoked through the source-register
        handles \texttt{[L-XX-N]} so the reader can independently
        verify what was retrieved versus what was read.
  \item Legal framing (\S{} 69e UrhG / EU 2009/24/EC) remains unsourced
        and is flagged as \texttt{[unverified-external]} in
        \texttt{docs/sources.md}.
\end{itemize}

\subsection{Disclaimers}
\label{sec:ai-disclosure-disclaimers}
\begin{itemize}
  \item \textbf{Not legal advice.} Any reference to copyright statutes
        or interoperability exemptions is descriptive, not prescriptive.
        Specific decisions about reverse-engineering activities should
        be evaluated by qualified legal counsel.
  \item \textbf{Not a coordinated vulnerability disclosure.} This paper
        documents prior community findings and integration work; it is
        not a coordinated disclosure for either Spider Farmer or
        EcoFlow products.
  \item \textbf{Tooling drift.} Identical prompts at later dates may
        produce non-identical outputs. The workflow and committed
        artifacts are the reproducible unit; AI outputs are not.
  \item \textbf{Live credentials.} \texttt{docs/sources.md} S-SF-5
        contains recovered live credentials from a community thread.
        These must be redacted before any public release of the paper
        or repository.
  \item \textbf{Fabricated-citation risk.} Empirical base rates for
        LLM-fabricated citations are 18\%--55\% for raw GPT outputs
        (\cref{sec:disc-sloppification}; L-SLOP-1, L-SLOP-2, L-SLOP-4).
        Every literature entry in this repository must be upgraded from
        \texttt{[lit-retrieved]} to \texttt{[lit-read]} before the
        paper is submitted for peer review.
  \item \textbf{Sloppification and model collapse.}
        \cref{sec:disc-sloppification} and
        \cref{sec:disc-model-collapse} explicitly acknowledge that
        AI-assisted research, when shipped without verification and
        disclosure, contributes to both the proximate sloppification
        of the scientific record (L-SLOP-7, L-SLOP-8) and the distal
        collapse of foundation models trained on it (L-MC-1, L-MC-3).
        The methodology in \cref{sec:methodology} is the author's
        best-effort response to that risk.
\end{itemize}

\subsection{Statement of independence and personal capacity}
\label{sec:independence}
This work is a hobbyist research project carried out by the author
(Florian Krebs, ORCID
\href{https://orcid.org/0000-0001-6033-801X}{0000-0001-6033-801X}) in a
strictly personal capacity. It is \textbf{not} part of, endorsed by,
funded by, supervised by, or representative of the views of any
employer, including the German Aerospace Center (DLR /
\textit{Deutsches Zentrum f\"ur Luft- und Raumfahrt}). The author's
day-job affiliation is acknowledged here only so the reader can rule it
out: no DLR resources, infrastructure, datasets, or
employer-confidential information were used in the preparation of this
paper or its underlying repository. The author's day-time research at
DLR concerns experimental data management (\texttt{shepard}) and is
unrelated to consumer-IoT reverse engineering. Any opinions expressed
are the author's own. The repository's \texttt{CITATION.cff},
\texttt{.zenodo.json}, \texttt{codemeta.json}, and \texttt{docs/fair.md}
all carry the affiliation \textbf{``Independent researcher (personal
capacity)''} in line with this statement.

\section*{Ethics and reproducibility statement}
\label{sec:ethics-statement}
This work follows the AI-assistance disclosure policy in
\texttt{CLAUDE\_CODE\_INSTRUCTIONS.md} and the ethics notes in
\texttt{docs/ethics.md}. Prompt logs and intermediate artifacts are
committed alongside the source. Recovered live credentials and device
identifiers are flagged for redaction prior to any public release.
This repository follows the FAIR data principles per
\texttt{docs/fair.md}; citation metadata is provided in
\texttt{CITATION.cff}, \texttt{.zenodo.json}, and \texttt{codemeta.json}.

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
